---
title: "Team Stats"
---

```{r}
#| echo: false
#| message: false
library(dplyr)
library(knitr)
library(plotly)

ordinal <- function(n) {
  if (is.na(n)) return("—")
  suffix <- if (n %% 100 %in% 11:13) "th" else
    switch(as.character(n %% 10), "1" = "st", "2" = "nd", "3" = "rd", "th")
  paste0(n, suffix)
}

stats_path <- "data/team-stats.csv"
events_path <- "data/team-event-results.csv"
have_data  <- file.exists(stats_path)
stats  <- if (have_data) read.csv(stats_path) else data.frame()
events <- if (file.exists(events_path)) read.csv(events_path) else data.frame()
```

::: {.callout-note}
**About this data.** These numbers come from [Duosmium](https://www.duosmium.org/results/), a community-maintained, open-source archive of Science Olympiad results — not an official database. From this:

- **Coverage is incomplete.** It only includes tournaments someone
  chose to upload, so a season or an invitational can be missing
  entirely.
:::

```{r}
#| echo: false
#| results: asis
if (!have_data || nrow(stats) == 0) {
  cat("_No data yet — run `Rscript R/update_duosmium_stats.R` to pull results from Duosmium._")
}
```

::: {.grid}

::: {.g-col-6 .g-col-md-3 .stat-card}
```{r}
#| echo: false
#| results: asis
best_reg <- if (have_data && any(stats$level == "Regionals", na.rm = TRUE)) {
  min(stats$rank[stats$level == "Regionals"], na.rm = TRUE)
} else NA
cat("<div class='stat-number'>", ordinal(best_reg), "</div>")
```
<div class="stat-label">Best Regional Finish</div>
:::

::: {.g-col-6 .g-col-md-3 .stat-card}
```{r}
#| echo: false
#| results: asis
best_state <- if (have_data && any(stats$level == "States", na.rm = TRUE)) {
  min(stats$rank[stats$level == "States"], na.rm = TRUE)
} else NA
cat("<div class='stat-number'>", ordinal(best_state), "</div>")
```
<div class="stat-label">Best State Finish</div>
:::

::: {.g-col-6 .g-col-md-3 .stat-card}
```{r}
#| echo: false
#| results: asis
total_medals <- if (have_data) sum(stats$event_medals, na.rm = TRUE) else 0
cat("<div class='stat-number'>", total_medals, "</div>")
```
<div class="stat-label">Career Event Medals</div>
:::

::: {.g-col-6 .g-col-md-3 .stat-card}
```{r}
#| echo: false
#| results: asis
n_tournaments <- if (have_data) nrow(stats) else 0
cat("<div class='stat-number'>", n_tournaments, "</div>")
```
<div class="stat-label">Tournaments on Record</div>
:::

:::

## Our Best Events

```{r}
#| echo: false
#| warning: false
if (nrow(events) == 0) {
  cat("Run the update script to populate this chart.")
} else {
  best_state_by_event <- events |>
    filter(level == "States") |>
    group_by(event) |>
    summarise(best_state = min(place, na.rm = TRUE), .groups = "drop")

  event_summary <- events |>
    group_by(event) |>
    summarise(
      medals = sum(medal, na.rm = TRUE),
      times  = n(),
      .groups = "drop"
    ) |>
    left_join(best_state_by_event, by = "event") |>
    mutate(
      best_state_label = vapply(best_state, function(n) if (is.na(n)) "never at States" else ordinal(n), character(1)),
      hover_text = paste0(
        "<b>", event, "</b><br>",
        "Medals: ", medals, "<br>",
        "Best States: ", best_state_label, "<br>",
        "Competed: ", times, "x"
      )
    ) |>
    arrange(medals) |>
    slice_tail(n = 15)

  plot_ly(
    event_summary,
    x = ~medals,
    y = ~factor(event, levels = event),
    type = "bar",
    orientation = "h",
    marker = list(color = "#E8720C"),
    text = ~hover_text,
    hoverinfo = "text",
    textposition = "none"
  ) |>
    layout(
      xaxis = list(title = "Career medals", tick0 = 0, dtick = 1, rangemode = "tozero"),
      yaxis = list(title = ""),
      margin = list(l = 180)
    ) |>
    config(displayModeBar = FALSE)
}
```

## Tournament History

```{r}
#| echo: false
if (have_data && nrow(stats) > 0) {
  stats |>
    arrange(desc(year)) |>
    transmute(
      Year = year,
      Tournament = tournament,
      Level = level,
      Div = division,
      Rank = paste0(rank, " / ", n_teams),
      Trophy = ifelse(trophy, "🏆", ""),
      `Event Medals` = event_medals
    ) |>
    kable()
} else {
  cat("Run the update script to populate this table.")
}
```